---
title: "Meta-analysis of Dalteparin vs. Apixaban"
author: "Luis Armando Figueroa & Oscar J. Ponce"
date: '2022-09-05'
output: github_document
---

```{r libraries, include=FALSE}
library(metafor)
library(openxlsx)
library(forestplot)
library(dplyr)

knitr::opts_chunk$set(fig.path = "8 Output Figures/", dev='svg') # dev = 'png'
```

```{r cleaning, include=FALSE}
dat <- read.xlsx("Extraccion de datos texto completo_updated.xlsx", sheet = 2)

dat_m <- subset(dat, Outcome == "Sangrado Mayor")
dat_m

dat_m2 <- dat_m[-3,]
dat_m2

dat_nm <- subset(dat, Outcome == "Sangrado no mayor")
dat_nm

dat_te <- subset(dat, Outcome == "rec TE")
dat_te

dat_te2 <- dat_te[-1,]
dat_te2
```

```{r or, include=FALSE}
dat_m <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=dat_m)
dat_m <- summary(dat_m)
dat_m

dat_m2 <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=dat_m2)
dat_m2 <- summary(dat_m2)
dat_m2


dat_nm <- escalc(measure="OR", ai=n1, bi=n2,
                ci=e1, di=e2, data=dat_nm)
dat_nm <- summary(dat_nm)
dat_nm

dat_te <- escalc(measure="OR", ai=n1, bi=n2,
                 ci=e1, di=e2, data=dat_te)
dat_te <- summary(dat_te)
dat_te

dat_te2 <- escalc(measure="OR", ai=n1, bi=n2,
                 ci=e1, di=e2, data=dat_te2)
dat_te2 <- summary(dat_te2)
dat_te2
```

```{r meta, include=FALSE}
meta_datm_reml <- rma(yi, vi, method="REML", data=dat_m, test='knha')
meta_datm_reml

meta_datm_pm <- rma(yi, vi, method="PM", data=dat_m, test='knha')
meta_datm_pm

meta_datm2_reml <- rma(yi, vi, method="REML", data=dat_m2, test='knha')
meta_datm2_reml

meta_datnm_reml <- rma(yi, vi, method="REML", data=dat_nm, test='knha')
meta_datnm_reml

meta_datnm_pm <- rma(yi, vi, method="PM", data=dat_nm, test='knha')
meta_datnm_pm

meta_datte_reml <- rma(yi, vi, method="REML", data=dat_te, test='knha')
meta_datte_reml

meta_datte_pm <- rma(yi, vi, method="PM", data=dat_te, test='knha')
meta_datte_pm

meta_datte2_reml <- rma(yi, vi, method="REML", data=dat_te2, test='knha')
meta_datte2_reml
```

```{r predict, include=FALSE}
meta_m <- predict(meta_datm_reml, transf = exp, digits = 2)
meta_m

metapm_m <- predict(meta_datm_pm, transf = exp, digits = 2)
metapm_m

meta_m2 <- predict(meta_datm2_reml, transf = exp, digits = 2)
meta_m2

meta_nm <- predict(meta_datnm_reml, transf = exp, digits = 2)
meta_nm

metapm_nm <- predict(meta_datnm_pm, transf = exp, digits = 2)
metapm_nm

meta_te <- predict(meta_datte_reml, transf = exp, digits = 2)
meta_te

metapm_te <- predict(meta_datte_pm, transf = exp, digits = 2)
metapm_te

meta_te2 <- predict(meta_datte2_reml, transf = exp, digits = 2)
meta_te2
```

<br>
<h2>Overall Forestplot</h2>

<details>

<summary><b>Figure 1 -</b> Odds of developing <b>Major Bleeding</b>, <b>Non-Major Bleeding</b> and <b>Recurrence of Venous Thromboembolism (VTE)</b> events in the Dalteparin group vs. the Apixaban group</summary>
<br>

```{r overall_graph_REML, echo=FALSE, fig.height = 6.5, fig.width = 13}
col1f <- c("Author", dat_m$Author, 
      paste("Overall Odds Ratio for", meta_datm_pm$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datm_pm$tau2, digits=2, format="f")), ", df = ", 
            (meta_datm_pm$parms),
            ", p ", (ifelse(meta_datm_pm$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datm_pm$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datm_pm$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", dat_nm$Author, 
      paste("Overall Odds Ratio for", meta_datnm_pm$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datnm_pm$tau2, digits=2, format="f")), ", df = ", 
            (meta_datnm_pm$parms),
            ", p ", (ifelse(meta_datnm_pm$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datnm_pm$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datnm_pm$I2, digits=1, format="f")), "%)"),
      NA, NA,
      "Author", dat_te$Author, 
      paste("Overall Odds Ratio for", meta_datte_pm$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datte_pm$tau2, digits=2, format="f")), ", df = ", 
            (meta_datte_pm$parms),
            ", p ", (ifelse(meta_datte_pm$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datte_pm$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datte_pm$I2, digits=1, format="f")), "%)"))

col2f <- c("Apixaban (n/N)",
      paste(dat_m$e1,"/", dat_m$n1), paste0(sum(dat_m$e1), " / ", sum(dat_m$n1)), NA, 
      NA, NA,
      "Apixaban (n/N)",
      paste(dat_nm$e1,"/", dat_nm$n1), paste0(sum(dat_nm$e1), " / ", sum(dat_nm$n1)), NA,
      NA, NA, 
      "Apixaban (n/N)",
      paste(dat_te$e1,"/", dat_te$n1), paste0(sum(dat_te$e1), " / ", sum(dat_te$n1)), NA)

col3f <- c("Dalteparin (n/N)",
      paste(dat_m$e2,"/", dat_m$n2), paste0(sum(dat_m$e2), " / ", sum(dat_m$n2)), NA,
      NA, NA,
      "Dalteparin (n/N)",
      paste(dat_nm$e2,"/", dat_nm$n2), paste0(sum(dat_nm$e2), " / ", sum(dat_nm$n2)), NA,
      NA, NA,
      "Dalteparin (n/N)",
      paste(dat_te$e2,"/", dat_te$n2), paste0(sum(dat_te$e2), " / ", sum(dat_te$n2)), NA)


col4f <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_m$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_m$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_m$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(metapm_m$pred, format = 'f', digits=2),
            "(", formatC(metapm_m$ci.lb, format = 'f', digits = 2),
            "-", formatC(metapm_m$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_nm$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_nm$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_nm$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(metapm_nm$pred, format = 'f', digits=2),
            "(", formatC(metapm_nm$ci.lb, format = 'f', digits = 2),
            "-", formatC(metapm_nm$ci.ub, format = 'f', digits = 2), ")"), NA,
          NA, NA,
          "Odds Ratio (95% CI)", paste0(formatC(exp(dat_te$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_te$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_te$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(metapm_te$pred, format = 'f', digits=2),
            "(", formatC(metapm_te$ci.lb, format = 'f', digits = 2),
            "-", formatC(metapm_te$ci.ub, format = 'f', digits = 2), ")"), NA)

col5f <- c("Weight(%)", paste(formatC(weights(meta_datm_pm), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datnm_pm), format='f', digits = 1),'%'), NA, NA,
           NA, NA,
           "Weight(%)", paste(formatC(weights(meta_datte_pm), format='f', digits = 1),'%'), NA, NA)

text1f <- cbind(col1f, col2f, col3f, col4f, col5f)


# Adding subtitles
subtitle1 <- c("Major Bleeding", rep(NA,4))
subtitle2 <- c("Non-Major Bleeding", rep(NA, 4))
subtitle3 <- c("Recurrence of Venous Thromboembolism (VTE)", rep(NA,4))

text1f <- rbind(text1f[1,], subtitle1, text1f[c(2:8),], subtitle2,
                text1f[c(10:16),], subtitle3, text1f[c(18:22),])
rownames(text1f) <- NULL


cf <- structure(list(
          mean = c(rep(NA, 2), exp(dat_m$yi), metapm_m$pred, rep(NA, 4), exp(dat_nm$yi), metapm_nm$pred, rep(NA, 4), exp(dat_te$yi), metapm_te$pred,NA),
          lower = c(rep(NA, 2), exp(dat_m$ci.lb), metapm_m$ci.lb, rep(NA, 4), exp(dat_nm$ci.lb), metapm_nm$ci.lb, rep(NA, 4), exp(dat_te$ci.lb), metapm_te$ci.lb, NA),
          upper = c(rep(NA, 2), exp(dat_m$ci.ub), metapm_m$ci.ub, rep(NA, 4), exp(dat_nm$ci.ub), metapm_nm$ci.ub, rep(NA, 4), exp(dat_te$ci.ub), metapm_te$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1f)),
          class = "data.frame")

sizes1f <- c(NA, NA, (weights(meta_datm_pm)*0.021), 1, rep(NA, 3),
             NA, (weights(meta_datnm_pm)*0.016), 1, rep(NA, 3), 
             NA, (weights(meta_datte_pm)*0.020), 1, NA)
names(sizes1f) <- NULL

plotf <- forestplot(text1f, 
             graph.pos = 4,
             zero = 1,
             cf,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1f,
             is.summary = c(T, T,F, F, F, T, T, T, T, T, F, F, F, T, T, T, T, T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.025, 0.25, 1, 4,  40),
             xlog=TRUE,
             clip = c(0.025, 40),
             grid = c(0.025, 0.25,  4, 40),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotf

```

</details>

<br>
<h2>Individual Forestplots</h2>


<details>

<summary><b>Figure 2 -</b> Major bleeding forestplot with PM estimator</summary>
<br>

```{r major_bleeding_graphs_pm, echo=FALSE, fig.height = 2, fig.width = 13}
col1mpm <- c("Author", dat_m$Author, 
      paste("Overall Odds Ratio for", meta_datm_pm$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datm_pm$tau2, digits=2, format="f")), ", df = ", 
            (meta_datm_pm$parms),
            ", p ", (ifelse(meta_datm_pm$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datm_pm$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datm_pm$I2, digits=1, format="f")), "%)"))

col2mpm <- c("Apixaban (n/N)",
      paste(dat_m$e1,"/", dat_m$n1), paste0(sum(dat_m$e1), " / ", sum(dat_m$n1)), NA)

col3mpm <- c("Dalteparin (n/N)",
      paste(dat_m$e2,"/", dat_m$n2), paste0(sum(dat_m$e2), " / ", sum(dat_m$n2)), NA)

col4mpm <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_m$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_m$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_m$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(metapm_m$pred, format = 'f', digits=2),
            "(", formatC(metapm_m$ci.lb, format = 'f', digits = 2),
            "-", formatC(metapm_m$ci.ub, format = 'f', digits = 2), ")"), NA)
col5mpm <- c("Weight(%)", paste(formatC(weights(meta_datm_pm), format='f', digits = 1),'%'), NA, NA)

text1mpm <- cbind(col1mpm, col2mpm, col3mpm, col4mpm, col5mpm)

cmpm <- structure(list(
          mean = c(rep(NA, 1), exp(dat_m$y), metapm_m$pred,NA),
          lower = c(rep(NA, 1), exp(dat_m$ci.lb), metapm_m$ci.lb, NA),
          upper = c(rep(NA, 1), exp(dat_m$ci.ub), metapm_m$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1mpm)),
          class = "data.frame")

sizes1mpm <- c(NA, (weights(meta_datm_pm)*0.010), 1, NA)

plotmpm <- forestplot(text1mpm,
             graph.pos = 4,
             zero = 1,
             cmpm,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1mpm,
             line.margin = 2,
             is.summary = c(T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.025, 0.25, 1, 4,  40),
             xlog=TRUE,
             clip = c(0.025, 40),
             grid = c(0.025, 0.25,  4, 40),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotmpm
```

</details>


<details>

<summary><b>Figure 3-</b> Major bleeding forestplot with REML estimator</summary>
<br>

```{r major_bleeding_graphs_reml, echo=FALSE, fig.height = 2, fig.width = 13}
col1m <- c("Author", dat_m$Author, 
      paste("Overall Odds Ratio for", meta_datm_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datm_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datm_reml$parms),
            ", p ", (ifelse(meta_datm_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datm_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datm_reml$I2, digits=1, format="f")), "%)"))

col2m <- c("Apixaban (n/N)",
      paste(dat_m$e1,"/", dat_m$n1), paste0(sum(dat_m$e1), " / ", sum(dat_m$n1)), NA)

col3m <- c("Dalteparin (n/N)",
      paste(dat_m$e2,"/", dat_m$n2), paste0(sum(dat_m$e2), " / ", sum(dat_m$n2)), NA)

col4m <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_m$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_m$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_m$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_m$pred, format = 'f', digits=2),
            "(", formatC(meta_m$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_m$ci.ub, format = 'f', digits = 2), ")"), NA)
col5m <- c("Weight(%)", paste(formatC(weights(meta_datm_reml), format='f', digits = 1),'%'), NA, NA)

text1m <- cbind(col1m, col2m, col3m, col4m, col5m)

cm <- structure(list(
          mean = c(rep(NA, 1), exp(dat_m$y), meta_m$pred,NA),
          lower = c(rep(NA, 1), exp(dat_m$ci.lb), meta_m$ci.lb, NA),
          upper = c(rep(NA, 1), exp(dat_m$ci.ub), meta_m$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1m)),
          class = "data.frame")

sizes1m <- c(NA, (weights(meta_datm_reml)*0.010), 1, NA)

plotm <- forestplot(text1m,
             graph.pos = 4,
             zero = 1,
             cm,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1m,
             line.margin = 2,
             is.summary = c(T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.025, 0.25, 1, 4,  40),
             xlog=TRUE,
             clip = c(0.025, 40),
             grid = c(0.025, 0.25,  4, 40),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotm
```

</details>


<details>

<summary><b>Figure 4 -</b> Non-Major Bleeding forestplot with PM estimator</summary>
<br>

```{r no_major_bleeding_graphs_pm, echo=FALSE, fig.height = 2, fig.width = 13}
col1nmpm <- c("Author", dat_nm$Author, 
      paste("Overall Odds Ratio for", meta_datnm_pm$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datnm_pm$tau2, digits=2, format="f")), ", df = ", 
            (meta_datnm_pm$parms),
            ", p ", (ifelse(meta_datnm_pm$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datnm_pm$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datnm_pm$I2, digits=1, format="f")), "%)"))

col2nmpm <- c("Apixaban (n/N)",
      paste(dat_nm$e1,"/", dat_nm$n1), paste0(sum(dat_nm$e1), " / ", sum(dat_nm$n1)), NA)

col3nmpm <- c("Dalteparin (n/N)",
      paste(dat_nm$e2,"/", dat_nm$n2), paste0(sum(dat_nm$e2), " / ", sum(dat_nm$n2)), NA)

col4nmpm <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_nm$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_nm$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_nm$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(metapm_nm$pred, format = 'f', digits=2),
            "(", formatC(metapm_nm$ci.lb, format = 'f', digits = 2),
            "-", formatC(metapm_nm$ci.ub, format = 'f', digits = 2), ")"), NA)
col5nmpm <- c("Weight(%)", paste(formatC(weights(meta_datnm_pm), format='f', digits = 1),'%'), NA, NA)

text1nmpm <- cbind(col1nmpm, col2nmpm, col3nmpm, col4nmpm, col5nmpm)

cnmpm <- structure(list(
          mean = c(rep(NA, 1), exp(dat_nm$y), metapm_nm$pred,NA),
          lower = c(rep(NA, 1), exp(dat_nm$ci.lb), metapm_nm$ci.lb, NA),
          upper = c(rep(NA, 1), exp(dat_nm$ci.ub), metapm_nm$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1nmpm)),
          class = "data.frame")

sizes1nmpm <- c(NA, (weights(meta_datnm_pm)*0.015), 1, NA)

plotnmpm <- forestplot(text1nmpm,
             graph.pos = 4,
             zero = 1,
             cnmpm,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1nmpm,
             line.margin = 2,
             is.summary = c(T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.1,0.25, 0.50, 1, 2, 4, 10),
             xlog=TRUE,
             clip = c(0.1, 10),
             grid = c(0.1,0.25, 0.50, 2, 4,10),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotnmpm
```

</details>



<details>

<summary><b>Figure 5 -</b> Non-Major Bleeding forestplot with REML estimator</summary>
<br>

```{r no_major_bleeding_graphs_reml, echo=FALSE, fig.height = 2, fig.width = 13}
col1nm <- c("Author", dat_nm$Author, 
      paste("Overall Odds Ratio for", meta_datnm_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datnm_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datnm_reml$parms),
            ", p ", (ifelse(meta_datnm_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datnm_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datnm_reml$I2, digits=1, format="f")), "%)"))

col2nm <- c("Apixaban (n/N)",
      paste(dat_nm$e1,"/", dat_nm$n1), paste0(sum(dat_nm$e1), " / ", sum(dat_nm$n1)), NA)

col3nm <- c("Dalteparin (n/N)",
      paste(dat_nm$e2,"/", dat_nm$n2), paste0(sum(dat_nm$e2), " / ", sum(dat_nm$n2)), NA)

col4nm <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_nm$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_nm$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_nm$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_nm$pred, format = 'f', digits=2),
            "(", formatC(meta_nm$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_nm$ci.ub, format = 'f', digits = 2), ")"), NA)

col5nm <- c("Weight(%)", paste(formatC(weights(meta_datnm_reml), format='f', digits = 1),'%'), NA, NA)

text1nm <- cbind(col1nm, col2nm, col3nm, col4nm, col5nm)

cnm <- structure(list(
          mean = c(rep(NA, 1), exp(dat_nm$y), meta_nm$pred,NA),
          lower = c(rep(NA, 1), exp(dat_nm$ci.lb), meta_nm$ci.lb, NA),
          upper = c(rep(NA, 1), exp(dat_nm$ci.ub), meta_nm$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1nm)),
          class = "data.frame")

sizes1nm <- c(NA, (weights(meta_datnm_reml)*0.015), 1, NA)

plotnm <- forestplot(text1nm,
             graph.pos = 4,
             zero = 1,
             cnm,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1nm,
             line.margin = 2,
             is.summary = c(T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.1,0.25, 0.50, 1, 2,4, 10),
             xlog=TRUE,
             clip = c(0.2, 10),
             grid = c(0.1,0.25, 0.50,  2,4,10),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotnm
```

</details>


<details>

<summary><b>Figure 6 -</b> Recurrence of VTE forestplot with PM estimator</summary>
<br>

```{r TE_recurrence_PM, echo=FALSE, fig.height = 2, fig.width = 13}
col1tepm <- c("Author", dat_te$Author, 
      paste("Overall Odds Ratio for", meta_datte_pm$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datte_pm$tau2, digits=2, format="f")), ", df = ", 
            (meta_datte_pm$parms),
            ", p ", (ifelse(meta_datte_pm$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datte_pm$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datte_pm$I2, digits=1, format="f")), "%)"))

col2tepm <- c("Apixaban (n/N)",
      paste(dat_te$e1,"/", dat_te$n1), paste0(sum(dat_te$e1), " / ", sum(dat_te$n1)), NA)

col3tepm <- c("Dalteparin (n/N)",
      paste(dat_te$e2,"/", dat_te$n2), paste0(sum(dat_te$e2), " / ", sum(dat_te$n2)), NA)

col4tepm <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_te$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_te$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_te$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(metapm_te$pred, format = 'f', digits=2),
            "(", formatC(metapm_te$ci.lb, format = 'f', digits = 2),
            "-", formatC(metapm_te$ci.ub, format = 'f', digits = 2), ")"), NA)
col5tepm <- c("Weight(%)", paste(formatC(weights(meta_datte_pm), format='f', digits = 1),'%'), NA, NA)

text1tepm <- cbind(col1tepm, col2tepm, col3tepm, col4tepm, col5tepm)

ctepm <- structure(list(
          mean = c(rep(NA, 1), exp(dat_te$y), metapm_te$pred,NA),
          lower = c(rep(NA, 1), exp(dat_te$ci.lb), metapm_te$ci.lb, NA),
          upper = c(rep(NA, 1), exp(dat_te$ci.ub), metapm_te$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1tepm)),
          class = "data.frame")

sizes1tepm <- c(NA, (weights(meta_datte_pm)*0.020), 1, NA)

plottepm <- forestplot(text1tepm,
             graph.pos = 4,
             zero = 1,
             ctepm,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1tepm,
             line.margin = 2,
             is.summary = c(T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.1, 0.30, 1, 4, 10, 40),
             xlog=TRUE,
             clip = c(0.1, 40),
             grid = c(0.1, 0.30,  4, 10, 40),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plottepm
```

</details>


<details>

<summary><b>Figure 7 -</b> Recurrence of VTE forestplot with REML estimator</summary>
<br>

```{r TE_recurrence_REML, echo=FALSE, fig.height = 2, fig.width = 13}
col1te <- c("Author", dat_te$Author, 
      paste("Overall Odds Ratio for", meta_datte_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datte_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datte_reml$parms),
            ", p ", (ifelse(meta_datte_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datte_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datte_reml$I2, digits=1, format="f")), "%)"))

col2te <- c("Apixaban (n/N)",
      paste(dat_te$e1,"/", dat_te$n1), paste0(sum(dat_te$e1), " / ", sum(dat_te$n1)), NA)

col3te <- c("Dalteparin (n/N)",
      paste(dat_te$e2,"/", dat_te$n2), paste0(sum(dat_te$e2), " / ", sum(dat_te$n2)), NA)

col4te <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_te$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_te$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_te$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_te$pred, format = 'f', digits=2),
            "(", formatC(meta_te$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_te$ci.ub, format = 'f', digits = 2), ")"), NA)

col5te <- c("Weight(%)", paste(formatC(weights(meta_datte_reml), format='f', digits = 1),'%'), NA, NA)

text1te <- cbind(col1te, col2te, col3te, col4te, col5te)

cte <- structure(list(
          mean = c(rep(NA, 1), exp(dat_te$y), meta_te$pred,NA),
          lower = c(rep(NA, 1), exp(dat_te$ci.lb), meta_te$ci.lb, NA),
          upper = c(rep(NA, 1), exp(dat_te$ci.ub), meta_te$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1te)),
          class = "data.frame")

sizes1te <- c(NA, (weights(meta_datte_reml)*0.020), 1, NA)

plotte <- forestplot(text1te,
             graph.pos = 4,
             zero = 1,
             cte,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1te,
             line.margin = 2,
             is.summary = c(T, F, F, F, T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.1, 0.30, 1, 4, 10, 40),
             xlog=TRUE,
             clip = c(0.1, 40),
             grid = c(0.1, 0.30,  4, 10, 40),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotte
```

</details>
